An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-06 EconGrowth-R-Functions.Rnw
Added a better comment about covariance calculations.

##############################
# Returns an xtable of covariance information for the specified country.
##
covarianceTable <- function(countryAbbrev){
  data <- loadData(countryAbbrev)
  if (countryAbbrev %in% countryAbbrevsU){
    # Calculate covariances among the typical variables.
    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
    # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
    # 1980-2011 for covariances among y, k, l, q, and x for developed economies
    # 1980-2000 for covariances involving u for developed economies
    # 1991-2011 for covariances among y, k, l, q, and x for developing economies
    covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
  } else {
    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
    covarResults <- cor(dataForCovar)
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
  }
  colnames(covarResults) <- names
  rownames(covarResults) <- names
  # Now make an xtable so it displays nicely
  covarXtable <- xtable(covarResults, 
                      caption=paste(countryAbbrev, "covariance table."), 
                      label=paste("tab:Covariance_", countryAbbrev, sep=""))
  return(covarXtable)
}

>>>>

##############################
# Returns an xtable of covariance information for the specified country.
##
covarianceTable <- function(countryAbbrev){
  data <- loadData(countryAbbrev)
  if (countryAbbrev %in% countryAbbrevsU){
    # Calculate covariances among the typical variables.
    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
    # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
    # 1980-2011 for covariances among y, k, l, q, and x for developed economies
    # 1980-2000 for covariances involving u for developed economies
    # 1991-2011 for covariances among y, k, l, q, and x for developing economies
    # The key here is the use="pairwise.complete.obs" argument.
    covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
  } else {
    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
    covarResults <- cor(dataForCovar)
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
  }
  colnames(covarResults) <- names
  rownames(covarResults) <- names
  # Now make an xtable so it displays nicely
  covarXtable <- xtable(covarResults, 
                      caption=paste(countryAbbrev, "covariance table."), 
                      label=paste("tab:Covariance_", countryAbbrev, sep=""))
  return(covarXtable)
}
